Supplementary materials to: Describing vocalizations in young children: A big data approach through citizen science annotations

### 2021-03-02 202010_jslhr/paper.Rmd
minor

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(dplyr)
library(ggplot2)
library(caret)
library(scales)
library(kableExtra)
library(huxtable) #merging cells in tab1
library(rel)
library(ggpubr)
library(lme4)
#knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.pos = "T")
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE)
```

@@

#document session info
capture.output(sessionInfo(),file="lastknit_session_info.txt")

>>>>

```{r setup, include = FALSE}
library(groundhog)
groundhog.day="2021-02-23"
pkgs=c('papaja','tidyverse','dplyr','ggplot2','caret','scales','kableExtra','rel','ggpubr','lme4','rmarkdown')
groundhog.library(pkgs, groundhog.day)

#knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.pos = "T")
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE)
```

@@

#document session info
capture.output(sessionInfo(),file="paper-lastknit_session_info.txt")

### 2021-03-02 202010_jslhr/sup_mat.Rmd
minor

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
library(tidyverse)
library(dplyr)
library(ggplot2)
library(caret)
library(scales)
library(kableExtra)
library(rel)
dodiv=function(x) x/sum(x, na.rm=T)
```

>>>>

```{r setup, include=FALSE}
library(groundhog)
groundhog.day="2021-02-23"
pkgs=c("knitr", 'tidyverse','dplyr','ggplot2','caret','scales','kableExtra','rel','rmarkdown')
groundhog.library(pkgs, groundhog.day)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)

dodiv=function(x) x/sum(x, na.rm=T)
```
